\documentclass[../main.tex]{subfiles}
\begin{document}


\cite{10096986}	L. Wang, R. Han and W. Feng, \textit{Combining the Silhouette and Skeleton Data for Gait Recognition}, [Online]. Available: \url{https://ieeexplore.ieee.org/abstract/document/10096986} (visited on 09/10/2025).


\cite{Zhu_2023_WACV}	Zhu, Haidong and Zheng, Zhaoheng and Nevatia, Ram, ``Gait Recognition Using 3-D Human Body Shape Inference" in \textit{Proceedings of the IEEE/CVF Winter Conference on Applications of Computer Vision (WACV)}, January, 2023, pp. 909-918.


\cite{Ma_2024_CVPR}	Ma, Kang and Fu, Ying and Cao, Chunshui and Hou, Saihui and Huang, Yongzhen and Zheng, Dezhi, ``Learning Visual Prompt for Gait Recognition" in \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, June, 2024, pp. 593-603.

\cite{Peng2024}	Peng, Y., Ma, K., Zhang, Y. et al, \textit{Learning rich features for gait recognition by integrating skeletons and silhouettes}. [Online]. Available: \url{https://doi.org/10.1007/s11042-023-15483-x} (visited on 09/10/2025).

\cite{10203341}	H. Dou, P. Zhang, W. Su, Y. Yu, Y. Lin and X. Li \textit{GaitGCI: Generative Counterfactual Intervention for Gait Recognition}, [Online]. Available: \url{https://ieeexplore.ieee.org/document/10203341} (visited on 06/11/2025).

\cite{9351667}	H. Chao, K. Wang, Y. He, J. Zhang and J. Feng \textit{GaitSet: Cross-View Gait Recognition Through Utilizing Gait As a Deep Set,}, [Online]. Available: \url{https://ieeexplore.ieee.org/document/9351667} (visited on 10/22/2025).

\end{document}